From big data to deep insight in developmental science

### 2015-07-07 wiley-big-data-devel/big-data.tex
more abt devel sci & big data

So, big data looms large in the minds of public agencies who fund most research on human development.
In recognizing this, we note that the recent focus on big data has a history longer than the 21st century \cite{Press2013a}. 
Indeed, developmental scientists have long recognized the importance of collecting and sharing data sets that are big along at least one dimension -- the number of individuals, number of time points sampled, or the number of measures collected.
In turn, researchers in developmental science have continued to pioneer advanced analytical techniques that unpack and explain developmental phenomena across multiple levels of analysis and across wide-ranging timescales \cite{CDS2014, QuantDev}.

>>>>

Clearly, big data looms large in the minds of public officials whose agenciesfund most research on human development.
In recognizing this, we note that the recent focus on big data has a history longer than the 21st century \cite{Press2013a}.
Indeed, developmental scientists have long recognized the importance of collecting and sharing data sets that are big along at least one dimension -- the number of individuals, number of time points sampled, or the number of measures collected.
In turn, researchers in developmental science have continued to pioneer advanced analytical techniques that unpack and explain developmental phenomena across multiple levels of analysis and across wide-ranging timescales \cite{CDS2014, QuantDev}.
Developmental scientists have also been at the vanguard of efforts to create ways to share research data that preserve privacy and uphold ethical research principles \cite{Adolph2012, AERA2011, AERAVideo2015, Bakeman2011, Databrary2015}.
